### 2022-02-07 README.Rmd
Deploying to gh-pages from @ gavinsimpson/gratia@d1446126f1bdb4afc6a55ce3f506382e1be54587 🚀

<!-- badges: start -->
[![R build status](https://github.com/gavinsimpson/gratia/workflows/R-CMD-check/badge.svg)](https://github.com/gavinsimpson/gratia/actions)
[![codecov.io](https://codecov.io/gh/gavinsimpson/gratia/branch/master/graph/badge.svg)](https://codecov.io/gh/gavinsimpson/gratia)
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/gratia)](https://cran.r-project.org/package=gratia)
[![CRAN Downloads](http://cranlogs.r-pkg.org/badges/grand-total/gratia)](http://cran.rstudio.com/web/packages/gratia/index.html)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R build status](https://github.com/gavinsimpson/gratia/workflows/R-CMD-check/badge.svg)](https://github.com/gavinsimpson/gratia/actions)
[![codecov.io](https://codecov.io/gh/gavinsimpson/gratia/branch/master/graph/badge.svg)](https://app.codecov.io/gh/gavinsimpson/gratia)
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/gratia)](https://cran.r-project.org/package=gratia)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/grand-total/gratia)](https://cran.r-project.org/package=gratia)
<!-- badges: end -->
